Prediction of Drinking Water Treatment Process Chemical Doses

### 2025-12-17 FinalPaper_DSCI445_Group4.Rmd
Edits made to output redundancies

---
title: "Prediction of Drinking Water Treatment Process Chemical Doses"
author: "Dawson Carney, Reece Carmody, Ethan Schilling, Joshua Tobey"
date: "17 December 2025"
output: pdf_document
toc: TRUE
---
CAUTION: Please uncomment any of the install.packages that aren't already installed.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#install.packages("zoo")
#install.packages("purrr")
#install.packages("kableExtra")
#install.packages("vip")
#install.packages("png")
#install.packages("grid")
#install.packages("discrim")
#install.packages("gt")
#install.packages("Metrics")
#install.packages("ranger")
#install.packages("randomForest")

@@

}
  performance <- performance %>% arrange(RMSE)
performance
```
Selecting the best RMSE:
```{r}
best_rmse <- min(performance$RMSE)
best_rmse
```
Display Plots of models' performance on test data:
```{r}
kable_table_pdf <- performance %>%
  # Use format = "latex" for PDF output
  kable("latex",
        booktabs = TRUE)

@@

gam_fit <- gam(
  FeCl_dose ~ s(Polymer_dose) + s(mean_Temp) + s(mean_pH) + s(mean_Conductivity) +
               s(mean_Turbidity) + s(Temp_lag1) + s(Temp_lag2) +
               s(pH_lag1) + s(pH_lag2) + s(Cond_lag1) + s(Cond_lag2) +
               s(Turb_lag1) + s(Turb_lag2),
  data = train
)

gam_fit |> tidy()
gam_fit |> glance()
```
```{r}
pred_df <- test %>% 
  mutate(pred = predict(gam_fit, newdata = test))

>>>>

---
title: "Prediction of Drinking Water Treatment Process Chemical Doses"
author: "Dawson Carney, Reece Carmody, Ethan Schilling, Joshua Tobey"
date: "17 December 2025"
output: pdf_document
toc: TRUE
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

}
  performance <- performance %>% arrange(RMSE)
```
Selecting the best RMSE:
```{r}
best_rmse <- min(performance$RMSE)
best_rmse
```
Display Plots of models' performance on test data:
```{r}
kable_table_pdf <- performance %>%
  # Use format = "latex" for PDF output
  kable("latex",
        booktabs = TRUE)

@@

gam_fit <- gam(
  FeCl_dose ~ s(Polymer_dose) + s(mean_Temp) + s(mean_pH) + s(mean_Conductivity) +
               s(mean_Turbidity) + s(Temp_lag1) + s(Temp_lag2) +
               s(pH_lag1) + s(pH_lag2) + s(Cond_lag1) + s(Cond_lag2) +
               s(Turb_lag1) + s(Turb_lag2),
  data = train
)
```
```{r}
pred_df <- test %>% 
  mutate(pred = predict(gam_fit, newdata = test))
